A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-04-03 paper/sections/categorization.tex
Minor updates to process and categories.

During the paper reading phase, the authors noted that a variety of themes were present amongst the extensions. 
For example, the paper ``Privacy-aware role-based access control'' \cite{ni2010privacy} brings in the notion of privacy directly in the title of the paper and the name of their model. 
Some papers presented this direct prouncement of their theme, while others were less obvious. 
Thus, the authors developed a set of guidelines to aide in determining a set of extension categories based upon observations during the paper reading phase. The guidelines were:

>>>>

During the paper reading phase, the authors noted that categorical themes were present among the extensions. 
For example, the paper ``Privacy-aware role-based access control'' \cite{ni2010privacy} brings in the notion of privacy directly within the title of the paper and the name of their model. 
Some papers presented this direct prouncement of a theme, while others were less obvious. 
Thus, the authors developed a set of guidelines to aide in determining a set of extension categories based upon observations during the paper reading phase. The guidelines were:
